Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
Added proof of Theorem 5

  Since $P_{S_1} = P_{\Downarrow S_1}$ and $P_{S_1} = P_{\Downarrow S_1}$, then 
  \begin{align*}
  P_{S_1}(s) &= \sum_{i=1}^n p_i * P_{SQ_i}(s)\\
  P_{S_2}(s) &= \sum_{j=1}^m q_m * P_{TQ_j}(s)
  \end{align*}
  hence
  \begin{align*}
  P_{S_1 \; |_p \; S_2}(s) &= p * (P_{S_1}(s)) + (1-p) * (P_{S_2}(s))\\
  &= p \left(\sum_{i=1}^n p_i * P_{SQ_i}(s)\right) + (1-p)\left(\sum_{j=1}^m q_m * P_{TQ_j}(s)\right)\\
  &= p * P_{\Downarrow S_1}(s) + (1-p) * P_{\Downarrow S_2}(s)\\
  &= P_{(\Downarrow S_1) \; |_p \; (\Downarrow S_2)}(s)
  \end{align*}
  which is what we wanted to show. This completes the proof.
\end{enumerate}
\end{proof}
\begin{theorem*}
  \label{thm:correct_entropy}
  If $\Regex$ is unambiguous and contains no empty subcomponents,
  $\EntropyOf{\Regex}$ is the entropy of $\mathcal{L}(\Regex)$.
\end{theorem*}
\begin{proof}
Given a discrete set $X$ and a probability distribution $P$ on $X$, we define the entropy $H(X)$ of $X$ by
$$H(X) = -\sum_{x \in X}P(x)\log_2{P(x)}$$
We prove the theorem by induction on $S$.
\begin{enumerate}
\item
($S = s$)

@@

\end{proof}
\end{document}

>>>>

  Since $P_{S_1} = P_{\Downarrow S_1}$ and $P_{S_1} = P_{\Downarrow S_1}$, then 
  \begin{align*}
  P_{S_1}(s) &= \sum_{i=1}^n p_i * P_{SQ_i}(s)\\
  P_{S_2}(s) &= \sum_{j=1}^m q_m * P_{TQ_j}(s)
  \end{align*}
  hence
  \begin{align*}
  P_{S_1 \; |_p \; S_2}(s) &= p * (P_{S_1}(s)) + (1-p) * (P_{S_2}(s))\\
  &= p \left(\sum_{i=1}^n p_i * P_{SQ_i}(s)\right) + (1-p)\left(\sum_{j=1}^m q_m * P_{TQ_j}(s)\right)\\
  &= p * P_{\Downarrow S_1}(s) + (1-p) * P_{\Downarrow S_2}(s)\\
  &= P_{(\Downarrow S_1) \; |_p \; (\Downarrow S_2)}(s)
  \end{align*}
  which is what we wanted to show. This completes the proof.
\end{enumerate}
\end{proof}
\begin{theorem}
  \label{CorrectEntropy}
  If $\Regex$ is unambiguous and contains no empty subcomponents,
  $\EntropyOf{\Regex}$ is the entropy of $\mathcal{L}(\Regex)$.
\end{theorem}
\begin{proof}
Given a discrete set $X$ and a probability distribution $P$ on $X$, we define the entropy $H(X)$ of $X$ by
$$H(X) = -\sum_{x \in X}P(x)\log_2{P(x)}$$
We prove the theorem by induction on $S$.
\begin{enumerate}
\item
($S = s$)

@@

\end{proof}
\begin{theorem}
If $DS$ is unambiguous, then $\EntropyOf{\DNFRegex}$ is the entropy of $P_{\DNFRegex}$.
\end{theorem}
\begin{proof}
By mutual induction over $DS$, $SQ$ and $A$ (the computations of the entropies follow the same pattern as the respective computations in \cref{CorrectEntropy}).
\begin{enumerate}
\item
($A = DS^{*p}$)

By the induction hypothesis $H(DS) = \mathbb{H}(DS)$, from which it follows that
$$H(DS^{*p}) = \frac{p}{1-p}(H(DS) - \log_2 p) - \log_2 (1-p) = \mathbb{H}(DS^{*p})$$
\item
($SQ = [s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]$)

By the induction hypothesis, hence by unambiguity $H(A_i) = \mathbb{H}(A_i)$, thus
$$H([s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]) = \sum_{i=1}^n H(A_i) = \sum_{i=1}^n \mathbb{H}(A_i) = \mathbb{H}([s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n])$$
\item
$(DS = \langle (SQ_1, p_1) \; | \; \ldots \; | \; (SQ_n, p_n)\rangle)$

By the induction hypothesis, $H(SQ_i, p_i) = \mathbb{H}(SQ_i, p_i)$. Using the formula
$$H(P) = H(m(P_1), \ldots m(P_n)) + \sum_{i=1}^n m(P_i)H(P_i)$$
if $P$ is a measure space satisfying $P = P_1 + \ldots + P_n$, then
\begin{align*}
H(\langle (SQ_1, p_1) \; | \; \ldots \; | \; (SQ_n, p_n)\rangle)
&= H(p_1, \ldots, p_n) + \sum_{i=1}^n p_i H(SQ_i, p_i)\\
&= \sum_{i=1}^n p_i \mathbb{H}(SQ_i, p_i) + p_i * \log_2 p_i\\
&= \mathbb{H}(\langle (SQ_1, p_1) \; | \; \ldots \; | \; (SQ_n, p_n)\rangle)
\end{align*}
\end{enumerate}
\end{proof}
\end{document}
